Digital Authoritarianism and Western Foreign Aid

### 2022-09-22 Paper.tex
Zotero
LitReview

\section*{Literature Review}

>>>>

\section*{Determinants of Aid}
\subsection*{Self-Interest versus Altruism}
Hoeffler, Outram: ``Our results indicate that all bilateral donors allocate aid according to their self-interest and recipient need''

Younas: Trade seems to account for donor behavior, along with priorities in human rights and miseries rather than poverty.

Wiseman, Young: Donors base behavior off of ``warm-glow''
